NumPy---Array Programming in Python

### 2020-01-26 body.tex
Minor edits

Users interact with NumPy arrays using {\em indexing} (to access
subarrays or individual elements), {\em operators} (e.g., $+$, $-$, $\times$, and $/$
for elementwise operations and $@$ for matrix multiplication), as well as {\em array-aware functions};
together, these provide an easily readable, expressive, high-level API for
array programming, while NumPy
deals with the underlying mechanics of making operations fast.

@@

The scientific Python ecosystem \fixme{(Fig.)} is composed of many different libraries.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
Matplotlib generates publication-ready figures and visualizations.
Employing these core array-aware libraries are widely used
technique-specific libraries\cite{SciPyProceedings_11}.
Finally, several domain-specific
libraries \cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}
are built on this diverse foundation of tooling.
This has made the scientific Python ecosystem popular for scientific
research.

>>>>

Users interact with NumPy arrays using {\em indexing} (to access
subarrays or individual elements), {\em operators} (e.g., $+$, $-$, $\times$
for elementwise operations and $@$ for matrix multiplication), as well as {\em array-aware functions};
together, these provide an easily readable, expressive, high-level API for
array programming, while NumPy
deals with the underlying mechanics of making operations fast.

@@

The scientific Python ecosystem \fixme{(Fig.)} is composed of many different libraries.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
Matplotlib generates publication-ready figures and visualizations.
Employing these array-aware libraries are widely used
technique-specific libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11}
and several domain-specific
libraries \cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
This has made the scientific Python ecosystem popular for scientific
research.
